Carbonate chemistry at Ny-Ålesund

### 2021-06-27 awipev-CO2.Rmd
Added pco2 thermal vs biology Takahashi

@@

```{r atmospheric CO2 Zeppelin, echo=FALSE, message= FALSE, warning=FALSE}
## Atmospheric CO2 Zeppelin
# downloaded 2020-08-19 from https://gaw.kishou.go.jp/search/file/0054-6001-1001-01-01-9999
# value:units : ppm
# value:long_name : measured_mole_fraction_of_trace_gas_in_dry_air
atm_co2_old <-
  read_delim(file = paste0(path, "atmospheric_co2_zeppelin/co2_zep_surface-insitu_54_9999-9999_hourly.txt"),
  delim = " ",
  comment = "#",
  #skip = 182,
  col_names = TRUE,
  na = "-999.999",
  ) %>%
  dplyr::mutate(co2_air = value,
  datetime = as_datetime(paste(paste(year, month, day, sep="-"), paste(hour, minute, second, sep="-"), sep = " "))) %>%
  dplyr::select(datetime, co2_air)

>>>>

## Takahashi thermal vs biological
```{r Takahashi thermal vs biological, include=FALSE}
# Select data
taka <- d_all %>% # just for this chunk
  dplyr::select(datetime, monthd, sal_fb, temp_insitu_11m, pco2_fb_insi_temp)

# In order to remove the temperature effect from the observed pCO2 , the observed pCO2 values are normalized to a constant temperature (annual mean) -- Takahashi et al. (2002)
temp_mean <- mean(taka$temp_insitu_11m, na.rm = TRUE)
taka <- taka %>% 
  dplyr::mutate(pco2_mean_temp = pco2_fb_insi_temp * exp(0.0423 * (temp_mean - temp_insitu_11m)))
d_pco2_bio <- max(taka$pco2_mean_temp, na.rm = TRUE) - min(taka$pco2_mean_temp, na.rm = TRUE)
d_pco2_temp <- max(taka$pco2_fb_insi_temp, na.rm = TRUE) - min(taka$pco2_fb_insi_temp, na.rm = TRUE)
temp_bio <- d_pco2_temp / d_pco2_bio
```

@@

```{r atmospheric CO2 Zeppelin, echo=FALSE, message= FALSE, warning=FALSE}
## Atmospheric CO2 Zeppelin
# downloaded 2020-08-19 from https://gaw.kishou.go.jp/search/file/0054-6001-1001-01-01-9999
# value:units : ppm
# value:long_name : measured_mole_fraction_of_trace_gas_in_dry_air
atm_co2_old <-
  read_delim(file = paste0(path, "atmospheric_co2_zeppelin_old/co2_zep_surface-insitu_54_9999-9999_hourly.txt"),
  delim = " ",
  comment = "#",
  #skip = 182,
  col_names = TRUE,
  na = "-999.999",
  ) %>%
  dplyr::mutate(co2_air = value,
  datetime = as_datetime(paste(paste(year, month, day, sep="-"), paste(hour, minute, second, sep="-"), sep = " "))) %>%
  dplyr::select(datetime, co2_air)
